A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-08-20 main.tex
3.6.5 - lambda selection method

 To evaluate the performance of penalized LMM methods in both scenarios, we consider exponential and dichotomous effect magnitudes with are concordant or discordant in nature, for a total of four distinct $\bgamma$ structures. We define concordant effects as those that are similar among genetically similar subpopulations, and discordant effects as those that are not. Figure \ref{fig:gamma_structures} displays a visual summary of these four coefficient structures. 
\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/gamma_structure.png}
    \caption{$\bgamma$ structures}
    \label{fig:gamma_structures}
\end{figure}

\subsubsection{$\lambda$ selection}
\anna{more details about how/why this lambda selection method - cite CV as bad for LMMs, BIC not great bc different likelihoods... tie this into evaluating performance of each method in terms of variable selection} The $\lambda$ that allowed for the first 50 variables to enter the model was selected for each method. 1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure.

%This method for selecting $\lambda$ was chosen to fairly compare the

%Cross-validation has generally been found to be inadvisable for penalized LMM methods \anna{cite thiiiiis}
%Using an information criterion such as BIC to select $\lambda$ is not comparable across methods since Lasso, PC-Lasso, LMM-Lasso-Rakitsch, and LMM-Lasso-ggmix methods each use a different likelihood.

>>>>

 To evaluate the performance of penalized LMM methods in both scenarios, we consider exponential and dichotomous effect magnitudes with are concordant or discordant in nature, for a total of four distinct $\bgamma$ structures. We define concordant effects as those that are similar among genetically similar subpopulations, and discordant effects as those that are not. Figure \ref{fig:gamma_structures} provides a visual summary of the four coefficient structures. 1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure. 
\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/gamma_structure.png}
    \caption{$\bgamma$ structures}
    \label{fig:gamma_structures}
\end{figure}

\subsubsection{$\lambda$ selection}
The $\lambda$ that allowed for the first 50 variables to enter the model was selected for each method, where 50 was the true number of causal SNPs. This method for selecting $\lambda$ was chosen in an attempt to compare the performance of all methods fairly, and as a strategy to evaluate methods in terms of variable selection, as it allows for direct comparison of the first 50 variables each method lets into the model. Alternative $\lambda$ selection methods were also considered. Cross-validation has been found to be inadvisable for LMMs, and in the presence of non-inedpendent samples as is the case here. While information criterion methods such as BIC present another option for selecting $\lambda$, they may be unstable in high dimensions. In addition, because Lasso, PC-Lasso, and LMM-Lasso use different likelihoods an information-criterion-based approach would not lend itself to comparable results across methods.
